### 2022-02-18 pre/pre.tex
more

Applying substitution to a literal is reduced to applying it to both sides of
the (dis)equation and extended pointwise to clauses. It is written in postfix notation
as $\sigmacl{l}$ and $\sigmacl{C}$.

@@

Two orders that are commonly used in superposition theorem proving are
Knuth-Bendix order (KBO) \cite[Sect.~5.4.4]{bn-98-tr-and-all-that} and
lexicographic path order (LPO) \cite[Sect.~5.4.2]{bn-98-tr-and-all-that}.
KBO assigns integer weights to symbols and uses precedence between symbols to
break eventual ties. LPO completely relies on precedence and inspects term
structure more closely to deterine the order.

>>>>

Applying substitution to a literal is reduced to applying it to both sides of
the (dis)equa\-tion and it is extended pointwise to clauses. It is written in postfix notation
as $\sigmacl{l}$ and $\sigmacl{C}$.

@@

Two orders that are commonly used in superposition theorem proving are
Knuth-Bendix order (KBO) \cite[Sect.~5.4.4]{bn-98-tr-and-all-that} and
lexicographic path order (LPO) \cite[Sect.~5.4.2]{bn-98-tr-and-all-that}.
KBO assigns integer weights to symbols and uses precedence between symbols to
break eventual ties. LPO entirely relies on precedence and inspects term
structure more closely to determine the order.
